Joint analysis of read count data

### 2020-09-09 combined_analysis/combine_all_data.Rmd
Fix Dx
add zenith

### Test Diagnosis * Sex
```{r differential.expression.interaction.DxSex}

@@

# BP by sex
L_BP = Lbase
L_SCZ['Reported_GenderMale'] = 1
L_SCZ['DxControl:Reported_GenderMale'] = -1
L_SCZ['DxBP'] = -1
L_SCZ['DxControl'] = 1

@@

### Test Region * Sex
```{r differential.expression.interaction.RegionSex, eval=FALSE}

>>>>

```{r gene_set_test.marginal}

library(zenith)

run_zenith = function(fit, coefs, gs.collection, n_genes_mi=10, n_genes_max=5000){

	# Map from Ensembl genes in geneSets_GO to 
	# from trimmed Ensembl names from RNA-seq data 
	geneSets.index = ids2indices( gs.collection, trim_ensembl_ids(rownames(fit)))

	# filter by size of gene set
	geneSets.index = geneSets.index[sapply(geneSets.index, function(x) (length(x) >= n_genes_min) & (length(x) <= n_genes_max)) ]

	# run zenith for each coefficient
	res = lapply( coefs, function(coef){
		zenith(fit, coef, geneSets.index, squaredStats=TRUE)
		} )
	names(res) = coefs

	res
}

# Load Gene Ontology database 
gs.GO = get_GeneOntology()
gs.MSigDB = get_MSigDB()

# convert from GeneSetCollection to list used by camera and zenith
gs.GO.collection = recodeToList( gs.GO )
gs.MSigDB.collection = recodeToList( gs.MSigDB )

res_zenith_marginal.GO = run_zenith( fit_marginal, colnames(L), gs.GO.collection )
res_zenith_marginal.MSigDB = run_zenith( fit_marginal, colnames(L), gs.MSigDB.collection )
```

### Test Diagnosis * Sex interaction
```{r differential.expression.interaction.DxSex}

@@

# SCZ by sex
L_SCZ = Lbase
L_SCZ['DxSCZ:Reported_GenderMale'] = 1
L_SCZ['Reported_GenderMale'] = -1
L_SCZ['DxSCZ'] = -1
L_SCZ['DxControl'] = 1 
# (A - B) - (C - D) = A - B - C + D

# BP by sex
L_BP = Lbase
L_BP['DxBP:Reported_GenderMale'] = 1
L_BP['Reported_GenderMale'] = -1
L_BP['DxBP'] = -1
L_BP['DxControl'] = 1

@@

### Test Region * Sex interaction
```{r differential.expression.interaction.RegionSex, eval=FALSE}
